

\documentclass[12pt]{article}
\usepackage{fullpage,enumitem,amsmath,amssymb,graphicx}

\title{Colloquium G - Concurrent Programming}
\author{Simon Hasir -- 7006072}

\usepackage{listings}

\begin{document}
    \maketitle
    \noindent
    \rule{\linewidth}{0.4pt}
             
    \section{TE-1}
    \begin{enumerate}[label=(\alph*)]
        \item Yes, but only if java is executed with the \textit{-ea} flag which enables Assertions.
        \item No, this behavior would involve too much overhead, but it's implemented for some java classes.
        \item No, not in the Bytecode.
        \item No, comments don't have any semantic, but it's good practice. ;)
        \item Kind of, \textit{await} just continues if it gets notified, BUT you have to check for the negation.
        \item No, Linked Listed have to be monitors as well.
        \item No, \textit{synchronized} can be applied almost as flexible, 
        the only problem is that only one lock per object is used.
        \item Yes 
        \item Yes, because multiple locks lead to smaller wait sets, which makes \textit{notifyAll()} faster.
        \item No, only if the class is a monitor that uses only implicit locking.
        \item No, not even if you can ensure that \textit{notify()} is called after \textit{wait()}, because Java could 
        wake up threads without signal as well $\Rightarrow$ you need a while loop. 
        \item Yes, safety violations can be found in finite executions and liveness problem only appear in infinite executions.
        \item No, see the above.
        \item No, \textit{run()} is a sequential function which you can execute in a new Thread
         with \textit{Thread.start()}
        \item Yes
        \item Yes, \textit{wait()} stops execution.
        \item Yes, \textit{notifyAll()} would be correct.
        \item No, you can only make methods and blocks synchronized.
        \item The \textit{signal()} call is valid, but the functionality may be impaired (e.g. thread that prints wrong result after to signals).
        \item Yes.
        \item True, once it crashes it can't recover. You can give a finite execution.
        \item No, it only sets the boolean flag \textit{interrupted} (fetchable with \textit{isInterrupted()})
        \item Yes
    \end{enumerate}
    \section{TG-2}
    \begin{enumerate}
        \item Monitor pseuCo -$>$ explicit locks Java
        \begin{enumerate}[label=(\alph*)]
            \item Replace \textit{monitor X} in pseuCo with \textit{class X} in Java.
            \item Add a \textit{private final}  intantice-wise lock $l$ in Java.
            \item Replace condition $c$ with $b$ in pseuCo with \textit{private final $c$ = l.newCondition()} in Java.
            \item Add lock at beginning of every function(wrapped in a try) and an unlock in the final block. Add trowInterruptException.
            \item Replace waitForCondition($c$) in pseuCo with while ($!b$) c.await(); in Java
        \end{enumerate}
        \item Explicit locks Java -$>$ Implicit Locks Java
        \begin{enumerate}[label=(\alph*)]
            \item remove explicit lock
            \item Replace locking and unlocking with the \textit{synchronized} keyword in the function definition.
            \item Make every field private
            \item Replace c.await with wait();
            \item Replace signal[All] with notify[All].
            \item Add some kind of indication which was condition should be the one that was triggered.
            \item Enjoy :)
        \end{enumerate}
    \end{enumerate}

    \section{TG-3}
    HashSet or Ringbuffer (of TreeSets) if you want good runtime, that save the counter for everyone in line,
    increment on overtake and check that nobody is at the cap. 
\end{document}

